---
output: rmarkdown::github_document
---

## Creating a new list for another movie

You found reviews of another, more recent, Jack Nicholson movie: The Departed!

| Scores | Comments               |
|--------|------------------------|
| 4.6    | I would watch it again |
| 5      | Amazing!               |
| 4.8    | I liked it             |
| 5      | One of the best movies |
| 4.2    | Fascinating plot       |

It would be useful to collect together all the pieces of information about the movie, like the title, actors, and reviews into a single variable. Since these pieces of data are different shapes, it is natural to combine them in a list variable.

`movie_title`, containing the title of the movie, and `movie_actors`, containing the names of some of the actors in the movie, are available in your workspace.

`@instructions`
- Create two vectors, called `scores` and `comments`, that contain the information from the reviews shown in the table.
- Find the average of the `scores` vector and save it as `avg_review`. 
- Combine the `scores` and `comments` vectors into a data frame called `reviews_df`. 
- Create a list, called `departed_list`, that contains the `movie_title`, `movie_actors`, reviews data frame as `reviews_df`, and the average review score as `avg_review`, and print it out.

`@hint`
- You'll use the `c()` function to create the vectors. 
- To find the average of a vector, pass the name of the vector to the `mean()` function. 
- Use the `data.frame()` function to create the `reviews_df` data frame.

`@pre_exercise_code`
```{r}
movie_title <- "The Departed"
movie_actors <- c("Leonardo DiCaprio", "Matt Damon", "Jack Nicholson","Mark Wahlberg","Vera Farmiga", "Martin Sheen")
```

`@sample_code`
```{r}
# Use the table from the exercise to define the comments and scores vectors
scores <- c(4.6, 5, 4.8, 5, ___
comments <- c("I would watch it again", "Amazing!", "I liked it", "One of the best movies", ___ 
# Save the average of the scores vector as avg_review
# Combine scores and comments into the reviews_df data frame
# Create and print out a list, called departed_list
```

`@solution`
```{r}
# Use the table from the exercise to define the comments and scores vectors
scores <- c(4.6, 5, 4.8, 5, 4.2)
comments <- c("I would watch it again", "Amazing!", "I liked it", "One of the best movies", "Fascinating plot")
# Save the average of the scores vector as avg_review
avg_review <- mean(scores)
# Combine scores and comments into the reviews_df data frame
reviews_df <- data.frame(scores, comments)
# Create and print out a list, called departed_list
departed_list <- list(movie_title, movie_actors, reviews_df, avg_review)
departed_list
```
